---
title: "R Notebook Lab 4"
output: html_notebook
#The mean length group. Its member will have to investigate the scaling of <d> as a function of n.
---


```{r}
# Load and install necessary packages
requiredPackages <-
   c("igraph",
     "ggplot2",
     "data.table",
     "knitr",
     "rstudioapi",
     "xtable")

for (pac in requiredPackages) {
   if (!require(pac,  character.only = TRUE)) {
      install.packages(pac, repos = "http://cran.rstudio.com")
      library(pac,  character.only = TRUE)
   }
}
rm(pac)
rm(requiredPackages)

# set pwd to current directory, must load rstudioapi before.
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

source("./summary_table.r")


```

```{r}
languages = c(
   "Arabic",
   "Basque",
   "Catalan",
   "Chinese",
   "Czech",
   "English",
   "Greek",
   "Hungarian",
   "Italian",
   "Turkish"
)

summary_tab = summary(languages)
print(summary_tab)
```

```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```


```{r}

```

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
